---
title: "Index"
format: html
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
            warnings = FALSE,
            message = FALSE,
            comment = "#>",
            #results = "hide",
            digits = 4,
            error = FALSE)
## clean the R environment
# graphics.off()
# rm(list = ls())
# freshr::freshr()
## load packages
library(here, quietly = TRUE)
library(tidyverse, quietly = TRUE)
library(gtsummary, quietly = TRUE)
library(flextable, quietly = TRUE)
## check the directory for the file
# here::dr_here()
here::set_here()
## the figure or results should be saved 
# paste0("foldername/Sfilename_workingresult_", 
#      Sys.Date(), ".filetype")
```

```{css, echo=FALSE}
.scroll-100 {
  max-height: 300px;
  max-width: 1000px;
  overflow-y: auto;
  background-color: inherit;
}
```

```{r, class.output="scroll-100"}

```


# Preface {.unnumbered}

This is a Quarto book for 2025 SCOPE DCC project.

The main documents are stored in this [link](https://olucdenver-my.sharepoint.com/shared?listurl=https%3A%2F%2Folucdenver%2Esharepoint%2Ecom%2Fsites%2FSCOPEDCC%2FShared%20Documents)


## Content {.unnumbered}

- Index
- Activity log
- Administrative information
  - Template
  - Study Information
  - Roles and responsibilities
  - Sap information
  - Project information
  - Investigator agreement
  - Signatures

- Study overview
  - Background
  - Aims and hypotheses
  - Interested variables
  - Causal dag
- Study methods
  - Study design
  - Sample size
  - Interim analyses
  - Data
  - Missing data
  - Simulations
- Statistical analysis
  - Significance
  - Descriptive statistics
  - Analysis methods
  - Additional
  - Sensitivity analysis
  - Exploratory analysis
  - Software
  - Others
- Tables and figures
  - Tables shells
  - Tables
  - Figures
  - Examples
- Additional information
  - Appendices
  - Glossary
  - Addenda
- References

## Folders 

- Data and Code 

- Figure Folder

- Style

- Output

- Report