---
title: "Read Me First"
format: html
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
            warnings = FALSE,
            message = FALSE,
            comment = "#>",
            #results = "hide",
            digits = 4,
            error = FALSE)
## clean the R environment
# graphics.off()
# rm(list = ls())
# freshr::freshr()
## load packages
library(here, quietly = TRUE)
library(tidyverse, quietly = TRUE)
library(gtsummary, quietly = TRUE)
library(flextable, quietly = TRUE)
## check the directory for the file
# here::dr_here()
here::set_here()
## the figure or results should be saved 
# paste0("foldername/Sfilename_workingresult_", 
#      Sys.Date(), ".filetype")
```

```{css, echo=FALSE}
.scroll-100 {
  max-height: 300px;
  max-width: 1000px;
  overflow-y: auto;
  background-color: inherit;
}
```

# Preface {.unnumbered}

This is a Quarto book for 2025 SCOPE DCC project.

The main documents are stored in this [link](https://olucdenver-my.sharepoint.com/shared?listurl=https%3A%2F%2Folucdenver%2Esharepoint%2Ecom%2Fsites%2FSCOPEDCC%2FShared%20Documents)

## Content {.unnumbered}

-   Activity Log
-   Administrative Information
    -   Analytic Plan Template
    -   Study Information
    -   Roles and Responsibilities
    -   SAP Information
    -   Project Information
    -   Investigator Agreement
    -   Signatures
-   Study Overview
    -   Background
    -   Aims and Hypotheses
    -   Interested Aariables
    -   Causal DAG
-   Study Methods
    -   Study Design
    -   Sample Size
    -   Interim Analyses
    -   Data
    -   Missing Data
    -   Simulations
-   Statistical Analysis
    -   Significance
    -   Descriptive Statistics
    -   Analysis Methods
    -   Additional
    -   Sensitivity Analysis
    -   Exploratory Analysis
    -   Software
    -   Others
-   Tables and Figures
    -   Tables Shells
    -   Tables
    -   Figures
    -   Examples
-   Additional Information
    -   Appendices
    -   Glossary
    -   Addenda
-   References

## Folders {.unnumbered}

### Files {.unnumbered}

```{r}
?list.files
list.files(path = "files", 
           # pattern = "_input.txt$", 
           recursive = TRUE)
```


### Data {.unnumbered}

```{r}
library(devtools)
library(usethis)
library(testthat)

use_data_raw("data-raw")
document()
# use_data()
```


### Codes {.unnumbered}

### Figures and Tables {.unnumbered}

### Style {.unnumbered}

### Outputs {.unnumbered}

### Reports {.unnumbered}
