---
title: "Aim1 Read Me First"
editor: source
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
            warnings = FALSE,
            message = FALSE,
            comment = "",
            #results = "hide",
            digits = 4,
            error = FALSE)
## clean the R environment
# graphics.off()
# rm(list = ls())
# freshr::freshr()
## load packages
library(here, quietly = TRUE)
library(tidyverse, quietly = TRUE)
library(gtsummary, quietly = TRUE)
library(flextable, quietly = TRUE)
## check the directory for the file
# here::dr_here()
here::set_here()
## the figure or results should be saved 
# paste0("foldername/Sfilename_workingresult_", 
#      Sys.Date(), ".filetype")
```

```{css, echo=FALSE}
.scroll-100 {
  max-height: 300px;
  max-width: 1000px;
  overflow-y: auto;
  background-color: inherit;
}
```

# Preface {.unnumbered}

This is a Quarto book for 2025 SCOPE DCC project.

*A Visual Tool to Help Develop a Statistical Analysis Plan for Randomized Trials in Palliative Care*

Collaboration with a statistician about the design of a statistical analysis plan can be enhanced by illustrating how statisticians conceptualize their task. This conceptualization can be represented by a directed acyclic graph (DAG), which illustrates the statistician’s approach and also provides an actionable tool to assist in the development of the plan.

Collaboration with a statistician can be enhanced by understanding how they conceptualize questions of study design and data analysis. In the language of constructivism: by explicitly encountering their “mental maps” of these topics. One such mental map pertains to the development of a statistical analysis plan (SAP), an outline of which is one of each team’s work products. Here, we use a figure to describe how statisticians typically conceptualize SAPs, and then illustrate how this figure can be used to develop an outline of a generic SAP for a randomized trial of a pain coping intervention in palliative care. It is our hope that making this conceptual framework explicit can help support more productive interactions between palliative care researchers and statisticians.

The main documents are stored in this [link](https://olucdenver-my.sharepoint.com/shared?listurl=https%3A%2F%2Folucdenver%2Esharepoint%2Ecom%2Fsites%2FSCOPEDCC%2FShared%20Documents)

## Content {.unnumbered}

```{r}
list.files(pattern = ".qmd$", 
           recursive = TRUE)
```

<!-- -   Activity Log -->

<!-- -   Administrative Information -->

<!--     -   Analytic Plan Template -->

<!--     -   Study Information -->

<!--     -   Roles and Responsibilities -->

<!--     -   SAP Information -->

<!--     -   Project Information -->

<!--     -   Investigator Agreement -->

<!--     -   Signatures -->

<!-- -   Study Overview -->

<!--     -   Background -->

<!--     -   Aims and Hypotheses -->

<!--     -   Interested Aariables -->

<!--     -   Causal DAG -->

<!-- -   Study Methods -->

<!--     -   Study Design -->

<!--     -   Sample Size -->

<!--     -   Interim Analyses -->

<!--     -   Data -->

<!--     -   Missing Data -->

<!--     -   Simulations -->

<!-- -   Statistical Analysis -->

<!--     -   Significance -->

<!--     -   Descriptive Statistics -->

<!--     -   Analysis Methods -->

<!--     -   Additional -->

<!--     -   Sensitivity Analysis -->

<!--     -   Exploratory Analysis -->

<!--     -   Software -->

<!--     -   Others -->

<!-- -   Tables and Figures -->

<!--     -   Tables Shells -->

<!--     -   Tables -->

<!--     -   Figures -->

<!--     -   Examples -->

<!-- -   Additional Information -->

<!--     -   Appendices -->

<!--     -   Glossary -->

<!--     -   Addenda -->

<!-- -   References -->

## Folders {.unnumbered}

### Documents {.unnumbered}

```{r}
?list.files
list.files(path = "files", 
           # pattern = "_input.txt$", 
           recursive = TRUE)
```

### Data {.unnumbered}

```{r}
library(devtools)
library(usethis)
library(testthat)

## including datasets into the package
# use_data_raw("data-raw")
# document()
# use_data()

list.files(path = "data-raw", 
           # pattern = "_input.txt$", 
           recursive = TRUE)

```

### Codes {.unnumbered}

```{r}
list.files(path = "R", 
           # pattern = "_input.txt$", 
           recursive = TRUE)
```

### Figures and Tables {.unnumbered}

```{r}
list.files(path = "figures", 
           # pattern = "_input.txt$", 
           recursive = TRUE)
```

### Reports {.unnumbered}
